---
name: José C.
surname: García Alanis
position: "PhD Candidate | Psycholgist | Data Analyst | Scientific Software Developer"
# address: "Department of Psychology, Philipps-University of Marburg"
profilepic: "./img/me.jpeg"
email: "alanis.jcg@gmail.com"
# twitter: JoiAlhaniz
github: JoseAlanis
linkedin: jcgalanis
aboutme: "Hi! I'm an experimental and clinical psychologist at the University of Marburg. My work lies at the interface between science and clinical practice, bridging basic research with the application of clincal interventions in the field. My research interests are focused on personal and situational influences on human brain function in relation to goal-directed behaviour. I have a background in statistical modelling and scientific software development using **Python** (e.g., NumPy, Pandas, SciPy, scikit-learn), **R**, and **Git**.  I'm also an active member of the open source community and an advocate of open, reproducible, and robust scientific practices."
date: "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(here)
library(dplyr)
library(glue)
library(tibble)
```

```{r get data, include=FALSE}
# scientific experience 
jobs <- read.table(here("data", "experience.tsv"), sep="\t", header = T)
# education
edu <- read.table(here("data", "education.tsv"), sep="\t", header = T)
# clinical work
clin <- read.table(here("data", "clinical.tsv"), sep="\t", header = T)
# skills
skills <- read.table(here("data", "skills.tsv"), sep="\t", header = T) %>% 
  group_by(category) %>% 
  mutate(skill = paste(skill, collapse = ", ")) %>% 
  unique
```

# Experience

## Scientific
```{r experience}
jobs %>% 
  detailed_entries(
    what = role,
    when = glue("{start_date}--{end_date}"),
    with = company,
    where = where,
    why = details)
```

## Clinical Work
```{r clinical}
clin %>%
  detailed_entries(
    what = role,
    when = glue("{start_date}--{end_date}"),
    where = loc,
    with = uni,
    why = details)
```

# Education 
```{r education}
edu %>% 
  detailed_entries( 
    what = degree,
    when = glue("{start_date}--{end_date}"),
    where = loc,
    with = uni,
    why = details)
```

\pagebreak

# Skills

```{r skills}
skills %>% 
  detailed_entries(what = skill, with = category)
```

# Workshops

```{r workshops}
tribble(
  ~ role, ~ course, ~ organisation, ~ country, ~ dates, ~ details,
  "Instructor / Organiser", 
  "Using Multivariate Statistics to Analyse EEG Data", 
  "Brainhack", 
  "Global", 
  "Nov. 2020", 
  "Virtual event. Researchers from across the globe work together on innovative projects.",
  
  "Instructor / Organiser",
  "Jupyter Nootebooks and Python essential training",
  "Brainhack Marburg", 
  "Germany", 
  "Nov. 2019", 
  "Hackathon for researchers to collaborate on open science / neuroimaging projects.",
  
  "Teaching Assistant", 
  "Machine Learning for Neuroscientists", 
  "DZNE", 
  "Magdeburg, Germany", 
  "Sep. 2019", 
  "Training with relevant neuroimaging software packages and tools for machine learning.",
  
  "Teaching Assistant", 
  "Library Carpentry", 
  "University Library Marburg", 
  "Germany", 
  "Jun. 2018", 
  " Create, analyse, and maintain sustainable data ressources with Python.") %>% 
  brief_entries(glue("\\textbf{<course>}: <role> (<organisation>, <country>) \\newline <details>", 
                     .open = "<", .close = ">"), paste0(dates, "\\newline"), .protect = FALSE)
```

# Grants and Awards

```{r Grants}
tribble(
  ~ grant, ~ organisation, ~ dates,
  "Reserach Fellowship (Marburg Model)", 
  "Philipps-Universität Marburg",
  "Oct. 2019",
  
  "DGPA Best Poster Award", 
  "44th DGPs/DGPA Tagung Psychologie und Gehirn conference (Gießen, Germany)",
  "Jun. 2018",
  
  "Travel Grant (DAAD-IPID4all)", 
  "Research Stay at Montreal Neurological Institut (Montreal, CA).",
  "Jan. 2016",
  
  "Travel Grant (DAAD-IPID4all)", 
  "55th Annual Meeting Society for Psychophysiological Research (Seattle, WA).",
  "Oct. 2015",

  "DAAD-STIBET",
  "Degree Completion Grant, Philipps-Universität Marburg.",
  "Jun. 2013",
  
 "DAAD-STIBET",
 "International Students Engagement Scholarship, Philipps-Universität Marburg.",
 "Jun. 2011") %>% 
  brief_entries(glue("\\textbf{<grant>}: <organisation>", 
                     .open = "<", .close = ">"), paste0(dates, ""), .protect = FALSE)
```


# Publications

1. Gau, R., Noble, S., Heuer, K., Bottenhorn, K. L., Bilgin, I. P., Yang, Y. F., ... & Marinazzo, D. (2021). Brainhack: Developing a culture of open, inclusive, community-driven neuroscience. *Neuron*. https://doi.org/10.1016/j.neuron.2021.04.001

2. Herholz, P., Vogelbacher, C., & **García Alanis., J. C.** (2020, November). G0RELLA/gorella_overview: initial alpha release (Version v0.0.1-alpha). Zenodo. http://doi.org/10.5281/zenodo.4276460

3. **García Alanis, J. C.**, Baker, T. E., Peper, M., & Chavanon, M. L. (2019). Social context effects on error-related brain activity are dependent on interpersonal and achievement-related traits. *Scientific reports, 9(1)*, 1-14. https://doi.org/10.1038/s41598-018-38417-2

4. Vainik, U., Baker, T. E., Dadar, M., Zeighami, Y., Michaud, A., Zhang, Y., ... & Dagher, A. (2018). Neurobehavioral correlates of obesity are largely heritable. *Proceedings of the National Academy of Sciences, 115(37)*, 9312-9317. https://doi.org/10.1073/pnas.1718206115

5. Bahn, D., Vesker, M., **García Alanis, J. C.**, Schwarzer, G., & Kauschke, C. (2017). Age-dependent positivity-bias in children’s processing of emotion terms. *Frontiers in psychology, 8*, 1268. https://doi.org/10.3389/fpsyg.2017.01268


