\begin{rubric}{Publications}

% -- ARTICLES --
\subrubric{Journal Articles}

\text{\hangindent=0.5in \textbf{Garc\'ia Alanis, J. C.}, Baker, T. E., Peper, M., \& Chavanon, M.-L. (\textit{in press}). Social context effects on error-related brain activity are dependent on interpersonal and achievement related traits. \par }

\text{\hangindent=0.5in \textbf{Garc\'ia Alanis, J. C.}, G\"uth, M. R., \& Peper, M. (\textit{in prep.}). Fronto-parietal oscillations reflect distinct proactive and reactive cognitive control mechanisms in the human brain. \par }

\text{\hangindent=0.5in G\"uth, M. R., \textbf{Garc\'ia Alanis, J. C.}, \& Peper, M. (\textit{in prep.}). Electrophysiological correlates of cognitive control during the reappraisal of pain in subjects with psychopathic personality traits. \par }

\text{\hangindent=0.5in Vainik, U., Baker, T. E., Dadar, M., Zeighami, Y., Michaud, A., Zhang, Y., \textbf{Garc\'ia Alanis, J. C.}, Misic, B., Collins, D. L., \& Dagher, A. (2018). Neurobehavioral correlates of obesity are largely heritable. \textit{Proceedings of the National Academy of Sciences}, \textit{115}(37), 9312. \href{https://doi.org/10.1073/pnas.1718206115}{https://doi.org/10.1073/pnas.1718206115} \par }

\text{\hangindent=0.5in Bahn, D., Vesker, M., \textbf{Garc\'ia Alanis, J. C.}, Schwarzer, G., \& Kauschke, C. (2017). Age-dependent Positivity-Bias in Children's Processing of Emotion Terms. \textit{Frontiers in Psychology}, \textit{8}, 1268. \href{https://doi.org/10.3389/fpsyg.2017.01268}{https://doi.org/10.3389/fpsyg.2017.01268} \par }


% -- TALKS --
\subrubric{Talks}

\text{\hangindent=0.5in \textbf{Garc\'ia Alanis, J. C.}, Herholz, P., Leinweber, K., Krause, E., \& Krippes, K. (2018, June). Library Carpentry, VDB-Landesverband Hessen (following: \href{https://www.liberquarterly.eu/article/10.18352/lq.10176/}{Library Carpentry: software skills training for library professionals}). Presentation at Philipps-Universität Marburg, Germany. \par }

\text{\hangindent=0.5in \textbf{Garc\'ia Alanis, J. C.}, (2018, June). Reproducible science workshop: Practical steps to improve the reproducibility of your research. In Erik M. M\"uller (Chair), B-EXP-Praktikum H: Modulation muskul\"arer Reflexe durch emotionale Reize (Open Science Expra). Presentation at the Department of Psychology, Philipps-Universität Marburg, Germany. \par }

\text{\hangindent=0.5in \textbf{Garc\'ia Alanis, J. C.}, (2016, February). Performance monitoring ERPs in the context of social interaction. In L. Fellows \& A. Dagher (Chair), Human Neuroimaging Lab Meeting. Presentation at the Montreal Neurological Institute (Canada), Montreal, QB. \par }

\text{\hangindent=0.5in \textbf{Garc\'ia Alanis, J. C.}, Chavanon, M.-L., Baker, T. E. \& Peper, M. (2015, September). Effects
of agentic and affiliative extraversion on electrophysiological measures of performance monitoring during social interaction. In D. Hagemeyer (Chair), Genetics and Biological Foundations. Symposium conducted at the DPPD 13. Arbeitstagung der Fachgruppe Differentielle Psychologie, Pers\"onlichkeitspsychologie und Psychologische Diagnostik (Germany), Mainz, RP. \par }


% -- POSTERS --
\subrubric{Posters (selected)}

\text{\hangindent=0.5in \textbf{Garc\'ia Alanis, J. C.}, G\"uth, M. R, \& Peper, M. (2018, May). Fronto-parietal oscillations reflect distinct proactive and reactive cognitive control mechanisms in the human brain. Poster presented at the 44th DGPs/DGPA Tagung Psychologie und Gehirn (Germany), Gie{\ss}en, HE. \par }

\text{\hangindent=0.5in \textbf{Garc\'ia Alanis, J. C.}, \& Peper, M. (2017, October). The time course of cognitive control: New insight under relaxed linearity assumptions. Poster presented at the 57th Annual Meeting of the Society for Psychophysiological Research (Austria), Vienna, W. \par }

\text{\hangindent=0.5in \textbf{Garc\'ia Alanis, J. C.}, Chavanon, M.-L., Musci, C., \& Peper, M. (2016, August). Fronto-parietal oscillatory patterns reflect preparatory top-down control and active behavioural adaption during a continuous performance task. Poster presentation at the 6th Motivation and Cognitive Control Symposium (Scotland), St. Andrews (FIF).  \par }

\text{\hangindent=0.5in \textbf{Garc\'ia Alanis, J. C.}, Chavanon, M.-L., Baker, T. E., \& Peper, M. (2015, October).  Agentic and affiliative extraversion differentially modulate the effects of two social contexts on electrophysiological measures of outcome monitoring. Poster presented at the 55th Annual Meeting of the Society for Psychophysiological Research (SPR), Seattle, WA. \par }

\text{\hangindent=0.5in \textbf{Garc\'ia Alanis, J. C.}, Chavanon, M.-L., Baker, T. E., \& Peper, M. (2015, June). Effects of interpersonal motivation and social context on error-related brain potentials. Poster presented at the DGPs/DGPA 41. Tagung Psychologie und Gehirn (Germany), Frankfurt am Main, HE. \par }

\text{\hangindent=0.5in G\"uth, M. R., \textbf{Garc\'ia Alanis, J. C.}, \& Peper, M. (2018, May). Keep calm and carry on: Reduced central-parietal positivity and increased resistance to emotional interference in subjects with psychopathic traits during a continuous performance task. Poster presented at the 44th DGPs/DGPA Tagung Psychologie und Gehirn (Germany), Gie{\ss}en, HE. \par }

\text{\hangindent=0.5in Ronoh, E. K., \textbf{Garc\'ia Alanis, J. C.}, Taentzer, G., \& Peper, M. (2018, May). Induction of unilateral neglect-like behaviour in healthy subjects: Exploring ambulatory assessment techniques. Poster presented at the 44th DGPs/DGPA Tagung Psychologie und Gehirn (Germany), Gie{\ss}en, HE. \par }

\text{\hangindent=0.5in Thiele, J.-C., \textbf{Garc\'ia Alanis, J. C.}, Molter, A., \& Peper, M. (2018, May). Risky behaviour in an Iowa Gambling Task is enhanced by an interpersonal competitive context. Poster presented at the 44th DGPs/DGPA Tagung Psychologie und Gehirn (Germany), Gie{\ss}en, HE. \par }

\text{\hangindent=0.5in Hammelrath, L., \textbf{Garc\'ia Alanis, J. C.}, G\"uth, M. R., Chavanon, M.-L., \& Peper, M. (2016, May). The cognitive consequences of supressing emotional expression - an ERP study. Poster presented at the DGPs/DGPA 42. Tagung Psychologie und Gehirn (Germany), Berlin, BE. \par }

\text{\hangindent=0.5in G\"uth, M. R., \textbf{Garc\'ia Alanis, J. C.}, Chavanon, M.-L., Hammelrath, L., \& Peper, M. (2016, May). Individual differences in reward sensitivity predict dynamic exertion of cognitive control during emotion suppression. Poster presented at the DGPs/DGPA 42. Tagung Psychologie und Gehirn (Germany), Berlin, BE. \par }


\end{rubric}
